Permutation Pattern matching in\\ $(213,231)$-avoiding permutations

### 2016-10-14 article.tex

@@

\begin{remark}
Every element of the set of \RLMax elements is above the elements
of the set of the \RLMin elements.
In other words, a wedge permutations
can be cut in half horizontally on the rightmost element such that the upper half contains a decreasing
subsequence and the lower half contains an increasing subsequence.
This shape the permutation as a $>$,
hence the name of wedge permutations.
See Figure~\ref{fig:shape of the permutation plus factor}.
\end{remark}

\begin{remark}
The partition gives a bijection between the set of wedge permutations of size $n$ where the elements are $1,\ldots,n$
and the set of binary word of size $n-1$.
The word $w$ which corresponds to $\pi$ is the word where each letter at position $i$
represents whether $\pi[i]$ is a \RLMax element or a \RLMin element.
We call this bijection $\bijection$.
\end{remark}

To figure out whether or not an element is a \RLMax element or a \RLMin element,
one has to run the whole permutation from left to right starting
from the position of the element, we give a corollary of lemma~\ref{lemma:first element is 1 or n}, to guest it in constant time.

\begin{corollary}
\label{corollary:max is ascent}
Let $\pi$ be a wedge permutation and $1 \leq i < n$. Then,
\begin{enumerate}
\item $\pi[i]$ is a \RLMin element if and only if $\pi[i]<\pi[i+1]$
\item $\pi[i]$ is a \RLMax element if and only if $\pi[i]>\pi[i+1]$ is a \RLMax
\end{enumerate}

@@

	\item If $\ptext[j] \in [\lb,\ub]$ and $\ppattern[i]$ is a \RLMin element then:
	$$
	\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ub}{i}{j}=
	\begin{cases}
		\bigcup_{\ell>j} \PM{\widetilde{\sigma}}{\ptext}{\ptext[j]+1}{\ub}{i+1}{\ell}
			& \text{if $\ppattern[i]$ is not underlined } \\
			& \text{ and $\ppattern[i]$ is not overlined} \\
		\bigcup_{\ell>j} \PM{\widetilde{\sigma}}{\ptext}{\ptext[j]+1}{\ub}{i+1}{\ell}
			& \text{if $\ppattern[i]$ is not underlined } \\
			& \text{ and $\overline{(\ppattern[i]-1)\ppattern[i]}$ or $^\ulcorner{\ppattern[i]}$}\\
			& \text{ appears in $\widetilde{\sigma}$}\\
			& \text{ and $\ptext[j]=\lb$} \\
		\PM{\widetilde{\sigma}}{\ptext}{\ptext[j]+1}{\ub}{i+1}{j+1}
			& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
			& \text{ appears in $\widetilde{\sigma}$}\\
			& \text{ and $\ppattern[i]$ is not overlined} \\
		\PM{\widetilde{\sigma}}{\ptext}{\ptext[j]+1}{\ub}{i+1}{j+1}
			& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
			& \text{ and $\overline{(\ppattern[i]-1)\ppattern[i]}$ or $^\ulcorner{\ppattern[i]}$}\\
			& \text{ appear in $\widetilde{\sigma}$}\\
			& \text{ and $\ptext[j]=\lb$} \\
		false & \text{otherwise}

	\end{cases}
	$$
	Remark that $\ppattern[i]$  can be matched to $\pi[j]$ because $\ptext[j] \in [\lb,\ub]$.
	Thus if $\ptext[j+1:]$ has an occurrence of $\widetilde{\sigma}[i+1:]$  with every element of the occurrence in $[\pi[j]+1,\ub]$ then
 	$\ptext[j:]$ has an occurrence $\widetilde{\sigma}[i:]$.
 	To decide the latter condition,
 	it is enough to know
 	 if there exists $\ell$, $j<\ell$ such that
	$\PM{\widetilde{\sigma}}{\ptext}{\ptext[j]+1}{\ub}{i+1}{\ell}$ is true.
	The first case corresponds to an occurrence without restriction on position and on value.
	The second case asks for the matching of $\ppattern[i]-1$ and $\ppattern[i]$ to be consecutive in value, but the matching of $\ppattern[i]-1$
	is $lb-1$ thus we want $\ptext[j]=\lb$.
	The third case asks for the matching of $\ppattern[i]$ and $\ppattern[i+1]$ to be consecutive in positions, thus the matching of $\ppattern[i+1]$ must be $\pi[j+1]$.
	The fourth case is a union of the second and third case.
%	Note that we do not have to consider the case where $\overline{\ppattern[i](\ppattern[i]+1)}$ appears in $\widetilde{\sigma}$
%	as the element $(\ppattern[i]+1)$ is on the right of $\ppattern[i]$
%	(see Lemma~\ref{lemma:after})
%	and thus will
%	be taken care
%	during the calls of $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i'}{*}$
%	for some $i<i'$.
%	Identically  we do not have to consider the case
%	where $\sigma[i-1]\sigma[i]$ appears in $\widetilde{\sigma}$

@@

	$$
	\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ub}{i}{j}=
	\begin{cases}
			\bigcup_{\ell>j} \PM{\widetilde{\sigma}}{\ptext}{\lb}{\ptext[j]-1}{i+1}{\ell}
				& \text{if $\ppattern[i]$ is not underlined } \\
				& \text{ and $\ppattern[i]$ is not overlined} \\
			\bigcup_{\ell>j} \PM{\widetilde{\sigma}}{\ptext}{\lb}{\ptext[j]-1}{i+1}{\ell}
				& \text{if $\ppattern[i]$ is not underlined } \\
				& \text{ and $\overline{\ppattern[i](\ppattern[i]+1)}$ or ${\ppattern[i]}^\urcorner$}\\
				& \text{ appear in $\widetilde{\sigma}$}\\
				& \text{ and $\ptext[j]=\ub$} \\
			\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}
				& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
				& \text{ appears in $\widetilde{\sigma}$}\\
				& \text{ and $\ppattern[i]$ is not overlined} \\
			\PM{\widetilde{\sigma}}{\ptext}{\lb}{\ptext[j]-1}{i+1}{j+1}
				& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
				& \text{ and $\overline{\ppattern[i](\ppattern[i]+1)}$ or ${\ppattern[i]}^\urcorner$}\\
				& \text{ appear in $\widetilde{\sigma}$}\\
				& \text{ and $\ptext[j]=\ub$} \\
			false & \text{otherwise}
	\end{cases}
	$$
	The same remark as the last case holds.
\end{itemize}

Remark that there are constraints that we do not concern given in
$\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$.
Especially in the case where $\sigma[i]$ is a \RLMin
the case where $\underline{\sigma[i-1]\sigma[i]}$,
$\overline{\ppattern[i](\ppattern[i]+1)}$
and every combination of the constraints
appear in $\widetilde{\sigma}$
are not in the conditions.
$\underline{\sigma[i-1]\sigma[i]}$ is not
in the conditions because it is
up to $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i-1}{*}$
to ensure that the elements corresponding to elements at position $i-1$ and $i$ in an occurrence are next to each other in position.
$\overline{\ppattern[i](\ppattern[i]+1)}$ is not
in the conditions because $\sigma[i]+1$ is on the right
of $\sigma[i]$ (see Lemma~\ref{lemma:after})
and thus will
be taken care
during the calls of $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i'}{*}$
for some $i<i'$.
In the same fashion,
when $\sigma[i]$ is a \RLMax $\underline{\sigma[i-1]\sigma[i]}$
do not appear in the conditions for the exact same reason
and $\overline{(\ppattern[i]-1)\ppattern[i]}$
because $\sigma[i]-1$ is on the right of $\sigma[i]$.

@@

\paragraph{Position Constraint.} There are 3 types of position constraints that can be added by underlined elements.
\begin{itemize}
	\item If $_\llcorner{\sigma[1]}$ appears in $\widetilde{\sigma}$ then the leftmost element of $\sigma$  must be matched to the leftmost element of $\pi$ ($\ppattern[1]$ is matched to $\ptext[1]$ in a occurrence of $\ppattern$ in $\ptext$). This constraint is satisfied by requiring that the occurrence starts at the leftmost element of $\ptext$: if  $\PM{\widetilde{\sigma}}{\ptext}{1}{n}{1}{1}$ is true.

	\item If ${\ppattern[k]}_\lrcorner$ appears in $\widetilde{\sigma}$ then the rightmost element $\sigma$ must be matched the rightmost element of $\pi$ ($\ppattern[k]$ is matched to $\ptext[n]$ on a occurrence of $\ppattern$ in $\ptext$). This constraint is checked in the base case.

@@

		\item If $\sigma[i]$ is a \RLMin element, then remark that:
		\begin{itemize}
			\item Every problem
			$\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i}{*}$ is true only if $\sigma[i]$ is matched to the element with value $\lb$ (by recursion).
			So it is enough to require that $\lb=1$.
			\item The recursive calls for $\sigma[1]$, $\ldots$, $\sigma[i-1]$
			do not change the lower bound as
			$\sigma[i]$ is the leftmost \RLMin element. Indeed if not, then there exists a \RLMin element $\sigma[i']$, $i'<i$ and by the shape of a wedge permutation $\sigma[i']<\sigma[i]$ which is not possible as $\sigma[i]$ must be the bottommost element.
			As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are \RLMax elements. Finally the recursive calls for \RLMax elements do not change the lower bound.
			\item The first call of the problem has for parameter $\lb=1$.
		\end{itemize}
		So $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ return true only if
		$\sigma[i]$ is matched to $1$.

		\item If $\sigma[i]$ is a \RLMax element then $i=k$ ($\sigma[i]$ is the rightmost element). Thus every $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ is a base case and is true only if $\sigma[i]$ is matched to $1$.

@@

		\item If $\sigma[i]$ is a \RLMax element, then remark that:
		\begin{itemize}
			\item Every problem
			$\PM{\widetilde{\sigma}}{\ptext}{*}{\ub}{i}{*}$ is true only if $\sigma[i]$ is matched to the element with value $\ub$ (by recursion).
			So it is enough to require that $\ub=n$.
			\item The recursive calls for $\sigma[1]$, $\ldots$, $\sigma[i-1]$
			do not change the upper bound as
			$\sigma[i]$ is the leftmost \RLMax element. Indeed if not, then there exists a \RLMax element $\sigma[i']$, $i'<i$ and by the shape of a wedge permutation $\sigma[i']>\sigma[i]$ which is not possible as $\sigma[i]$ must be the topmost element.
			As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are \RLMin elements. Finally the recursive calls for \RLMin elements do not change the upper bound.
			\item The first call of the problem has for parameter $\ub=n$.
		\end{itemize}
		So $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ return true only if
		$\sigma[i]$ is matched to $n$.

		\item If $\sigma[i]$ is a \RLMin element then $i=k$ ($\sigma[i]$ is the rightmost element). Thus every $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ is a base case and is true if $\sigma[i]$ is matched to $n$.

@@

			\item If $\ppattern[i]$ is a \RLMin element, $\ppattern[i']$ is a \RLMax element and $i<i'$ (remark that this case is symmetric to the case where $\ppattern[i]$ is a \RLMax element, $\ppattern[i']$ is a \RLMin element and $i'<i$), then
			remark that
			\begin{itemize}
				\item $i'=k$, indeed if $i'$ is not the right most element, there would exist an element between
				$\sigma[i]$ and $\sigma[i']$. So every recursive call
				$\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i'}{*}$
				is solved as a base case. So $\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i'}{*}$ is true only if $\sigma[i']$ is matched to the element with $\lb$.
				\item The recursive calls for $\sigma[i+1]$, $\ldots$, $\sigma[i'-1]$ do not change the lower bound.
				Indeed $\ppattern[i]$ is the rightmost \RLMin.
				So $\sigma[i+1]$, $\sigma[i+2]$, $\ldots$, $\sigma[i'-1]$ are \RLMax elements. Moreover
				recursive calls for a \RLMax do not change the lower bound.
				\item $\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i}{*}$ sets
				the $\lb$ to $\ptext[j]+1$ and matches $\sigma[i]$ to $\ptext[j]$.
			\end{itemize}
			So $\sigma[i]$ is matched to $\ptext[j]$ and
			$\sigma[i']$ is matched to $\ptext[j]+1$.

@@

				\item  Every recursive call $\PM{\widetilde{\sigma}}{\ptext}{\lb}{*}{i'}{*}$ is true only if $\sigma[i']$ is matched to the element with value $\lb$.

				\item  The recursive calls for $\sigma[i+1]$, $\ldots$, $\sigma[i'-1]$ do not change the lower bound. Indeed
				from lemma~\ref{lemma:ascentDescentAscent}, $\sigma[i+1]$,  $\ldots$, $\sigma[i'-1]$ are \RLMax elements. Finally the recursive calls for \RLMax elements do not change the lower bound.

				\item $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i}{*}$ sets $\lb$ to $\ptext[j]+1$ and matches $\sigma[i]$ to $\ptext[j]$.

@@

				\item  Every recursive call $\PM{\widetilde{\sigma}}{\ptext}{*}{\ub}{i}{*}$ is true only if $\sigma[i]$ is matched to the element with value $\ub$.

				\item  The recursive calls for $\sigma[i+1]$, $\ldots$, $\sigma[i'-1]$ do not change the upper bound. Indeed
				from lemma~\ref{lemma:ascentDescentAscent}, $\sigma[i+1]$,  $\ldots$, $\sigma[i'-1]$ are \RLMin elements. Finally the recursive calls for \RLMin elements do not change the upper bound.

				\item $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i'}{*}$ sets $\ub$ to $\ptext[j]-1$ and matches $\sigma[i']$ to $\ptext[j]$.

>>>>

As a consequence, a wedge permutation can be partitioned 
into three sets: the set of RLMax elements, the set of RLMin elements and the 
rightmost element which can be both a RLMax element and a RLMin element. 
The partition gives a bijection between the set of wedge permutations of size $n$ with elements $1,\ldots,n$
and the set of binary words of size $n-1$.
The word $w$ which corresponds to $\pi$ is the word where each letter at position $i$ 
represents whether $\pi[i]$ is a RLMax element or a RLMin element.
We call this bijection $\bijection$.

@@

\begin{remark}
We can draw a horizontally line (passing thought the rightmost element) on a wedge permutations  such that the upper half contains only a  decreasing  
subsequence and the lower half contains only an increasing subsequence.
This shape the permutation as a $>$, 
hence the name of wedge permutations. 
See Figure~\ref{fig:shape of the permutation plus factor}.
\end{remark}

For any permutation, to figure out whether or not an element is a RLMax element or a RLMin element,
one has to run the whole permutation from left to right starting 
from the position of the element, we give a corollary of lemma~\ref{lemma:first element is 1 or n}, to guest it in constant time for a wedge permutation.

\begin{corollary}
\label{corollary:max is ascent}
Let $\pi$ be a wedge permutation and $1 \leq i < n$. Then,
\begin{enumerate}
\item $\pi[i]$ is a RLMin element if and only if $\pi[i]<\pi[i+1]$
\item $\pi[i]$ is a RLMax element if and only if $\pi[i]>\pi[i+1]$
\end{enumerate}

@@

	\item If $\ptext[j] \in [\lb,\ub]$ and $\ppattern[i]$ is a \RLMin element then:
	$$
	\PM^{\widetilde{\sigma}}_{\ptext}(\lb,\ub,i,j)=
	\begin{cases}
		\bigcup_{\ell>j} \PM^{\widetilde{\sigma}}_{\ptext}(\ptext[j]+1,\ub,i+1,\ell)
			& \text{if $\ppattern[i]$ is not underlined } \\
			& \text{ and $\ppattern[i]$ is not overlined} \\
		\bigcup_{\ell>j} \PM^{\widetilde{\sigma}}_{\ptext}(\ptext[j]+1,\ub,i+1,\ell)
			& \text{if $\ppattern[i]$ is not underlined } \\
			& \text{ and $\overline{(\ppattern[i]-1)\ppattern[i]}$ or $^\ulcorner{\ppattern[i]}$}\\
			& \text{ appears in $\widetilde{\sigma}$}\\
			& \text{ and $\ptext[j]=\lb$} \\
		\PM^{\widetilde{\sigma}}_{\ptext}(\ptext[j]+1,\ub,i+1,j+1)
			& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
			& \text{ appears in $\widetilde{\sigma}$}\\
			& \text{ and $\ppattern[i]$ is not overlined} \\			
		\PM^{\widetilde{\sigma}}_{\ptext}(\ptext[j]+1,\ub,i+1,j+1)
			& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
			& \text{ and $\overline{(\ppattern[i]-1)\ppattern[i]}$ or $^\ulcorner{\ppattern[i]}$}\\
			& \text{ appear in $\widetilde{\sigma}$}\\
			& \text{ and $\ptext[j]=\lb$} \\
		false & \text{otherwise}

	\end{cases}
	$$
	Remark that $\ppattern[i]$  can be matched to $\pi[j]$ because $\ptext[j] \in [\lb,\ub]$.
	Thus if $\ptext[j+1:]$ has an occurrence of $\widetilde{\sigma}[i+1:]$  with every element of the occurrence in $[\pi[j]+1,\ub]$ then
 	$\ptext[j:]$ has an occurrence $\widetilde{\sigma}[i:]$.
 	To decide the latter condition,
 	it is enough to know
 	 if there exists $\ell$, $j<\ell$ such that
	$\PM^{\widetilde{\sigma}}_{\ptext}(\ptext[j]+1,\ub,i+1,\ell)$ is true.
	The first case corresponds to an occurrence without restriction on position and on value. 
	The second case asks for the matching of $\ppattern[i]-1$ and $\ppattern[i]$ to be consecutive in value, but the matching of $\ppattern[i]-1$
	is $lb-1$ thus we want $\ptext[j]=\lb$.
	The third case asks for the matching of $\ppattern[i]$ and $\ppattern[i+1]$ to be consecutive in positions, thus the matching of $\ppattern[i+1]$ must be $\pi[j+1]$.
	The fourth case is a union of the second and third case.
%	Note that we do not have to consider the case where $\overline{\ppattern[i](\ppattern[i]+1)}$ appears in $\widetilde{\sigma}$
%	as the element $(\ppattern[i]+1)$ is on the right of $\ppattern[i]$
%	(see Lemma~\ref{lemma:after})
%	and thus will
%	be taken care
%	during the calls of $\PM{\widetilde{\sigma}}{\ptext}{*}{*}{i'}{*}$
%	for some $i<i'$.
%	Identically  we do not have to consider the case
%	where $\sigma[i-1]\sigma[i]$ appears in $\widetilde{\sigma}$

@@

	$$
	\PM^{\widetilde{\sigma}}_{\ptext}(\lb,\ub,i,j)=
	\begin{cases}
			\bigcup_{\ell>j} \PM^{\widetilde{\sigma}}_{\ptext}(\lb,\ptext[j]-1,i+1,\ell)
				& \text{if $\ppattern[i]$ is not underlined } \\
				& \text{ and $\ppattern[i]$ is not overlined} \\
			\bigcup_{\ell>j} \PM^{\widetilde{\sigma}}_{\ptext}(\lb,\ptext[j]-1,i+1,\ell)
				& \text{if $\ppattern[i]$ is not underlined } \\
				& \text{ and $\overline{\ppattern[i](\ppattern[i]+1)}$ or ${\ppattern[i]}^\urcorner$}\\
				& \text{ appear in $\widetilde{\sigma}$}\\
				& \text{ and $\ptext[j]=\ub$} \\
			\PM^{\widetilde{\sigma}}_{\ptext}(\lb,\ptext[j]-1,i+1,j+1)
				& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
				& \text{ appears in $\widetilde{\sigma}$}\\
				& \text{ and $\ppattern[i]$ is not overlined} \\				
			\PM^{\widetilde{\sigma}}_{\ptext}(\lb,\ptext[j]-1,i+1,j+1)

				& \text{if $\underline{\ppattern[i]\ppattern[i+1]}$ } \\
				& \text{ and $\overline{\ppattern[i](\ppattern[i]+1)}$ or ${\ppattern[i]}^\urcorner$}\\
				& \text{ appear in $\widetilde{\sigma}$}\\
				& \text{ and $\ptext[j]=\ub$} \\
			false & \text{otherwise}
	\end{cases}
	$$
	The same remark as the last case holds.
\end{itemize}

Remark that there are constraints that we do not concern given in
$\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i,*)$.
Especially in the case where $\sigma[i]$ is a \RLMin
the case where $\underline{\sigma[i-1]\sigma[i]}$,
$\overline{\ppattern[i](\ppattern[i]+1)}$
and every combination of the constraints
appear in $\widetilde{\sigma}$
are not in the conditions.
$\underline{\sigma[i-1]\sigma[i]}$ is not
in the conditions because it is
up to $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i-1,*)$
to ensure that the elements corresponding to elements at position $i-1$ and $i$ in an occurrence are next to each other in position.
$\overline{\ppattern[i](\ppattern[i]+1)}$ is not
in the conditions because $\sigma[i]+1$ is on the right
of $\sigma[i]$ (see Lemma~\ref{lemma:after})
and thus will
be taken care
during the calls of $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i',*)$
for some $i<i'$.
In the same fashion,
when $\sigma[i]$ is a \RLMax $\underline{\sigma[i-1]\sigma[i]}$
do not appear in the conditions for the exact same reason
and $\overline{(\ppattern[i]-1)\ppattern[i]}$
because $\sigma[i]-1$ is on the right of $\sigma[i]$.

@@

\paragraph{Position Constraint.} There are 3 types of position constraints that can be added by underlined elements.

\begin{itemize} 
	\item If $_\llcorner{\sigma[1]}$ appears in $\widetilde{\sigma}$ then the leftmost element of $\sigma$  must be matched to the leftmost element of $\pi$ ($\ppattern[1]$ is matched to $\ptext[1]$ in a occurrence of $\ppattern$ in $\ptext$). This constraint is satisfied by requiring that the occurrence starts at the leftmost element of $\ptext$: if  $\PM^{\widetilde{\sigma}}_{\ptext}(1,n,1,1)$ is true.	
	\item If ${\ppattern[k]}_\lrcorner$ appears in $\widetilde{\sigma}$ then the rightmost element $\sigma$ must be matched the rightmost element of $\pi$ ($\ppattern[k]$ is matched to $\ptext[n]$ on a occurrence of $\ppattern$ in $\ptext$). This constraint is checked in the base case.

@@

		\item If $\sigma[i]$ is a \RLMin element, then remark that:
		\begin{itemize}
			\item Every problem 
			$\PM^{\widetilde{\sigma}}_{\ptext}(\lb,*,i,*)$ is true only if $\sigma[i]$ is matched to the element with value $\lb$ (by recursion).
			So it is enough to require that $\lb=1$.
			\item The recursive calls for $\sigma[1]$, $\ldots$, $\sigma[i-1]$
			do not change the lower bound as
			$\sigma[i]$ is the leftmost RLMin element. Indeed if not, then there exists a RLMin element $\sigma[i']$, $i'<i$ and by the shape of a wedge permutation $\sigma[i']<\sigma[i]$ which is not possible as $\sigma[i]$ must be the bottommost element. 
			As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are RLMax elements. Finally the recursive calls for RLMax elements do not change the lower bound.
			\item The first call of the problem has for parameter $\lb=1$. 
		\end{itemize} 
		So $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i,*)$ return true only if 
		$\sigma[i]$ is matched to $1$.

		\item If $\sigma[i]$ is a RLMax element then $i=k$ ($\sigma[i]$ is the rightmost element). Thus every $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i,*)$ is a base case and is true only if $\sigma[i]$ is matched to $1$.

@@

		\item If $\sigma[i]$ is a \RLMax element, then remark that:
		\begin{itemize}
			\item Every problem 
			$\PM^{\widetilde{\sigma}}_{\ptext}(*,\ub,i,*)$ is true only if $\sigma[i]$ is matched to the element with value $\ub$ (by recursion).
			So it is enough to require that $\ub=n$.
			\item The recursive calls for $\sigma[1]$, $\ldots$, $\sigma[i-1]$
			do not change the upper bound as
			$\sigma[i]$ is the leftmost RLMax element. Indeed if not, then there exists a RLMax element $\sigma[i']$, $i'<i$ and by the shape of a wedge permutation $\sigma[i']>\sigma[i]$ which is not possible as $\sigma[i]$ must be the topmost element. 
			As a consequence $\sigma[1]$, $\ldots$, $\sigma[i-1]$ are RLMin elements. Finally the recursive calls for RLMin elements do not change the upper bound.
			\item The first call of the problem has for parameter $\ub=n$. 
		\end{itemize} 
		So $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i,*)$ return true only if 
		$\sigma[i]$ is matched to $n$.

		\item If $\sigma[i]$ is a RLMin element then $i=k$ ($\sigma[i]$ is the rightmost element). Thus every $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i,*)$ is a base case and is true if $\sigma[i]$ is matched to $n$.

@@

			\item If $\ppattern[i]$ is a \RLMin element, $\ppattern[i']$ is a \RLMax element and $i<i'$ (remark that this case is symmetric to the case where $\ppattern[i]$ is a \RLMax element, $\ppattern[i']$ is a \RLMin element and $i'<i$), then
			remark that
			\begin{itemize}
				\item $i'=k$, indeed if $i'$ is not the right most element, there would exist an element between
				$\sigma[i]$ and $\sigma[i']$. So every recursive call
				$\PM^{\widetilde{\sigma}}_{\ptext}(\lb,*,i',*)$
				is solved as a base case. So $\PM^{\widetilde{\sigma}}_{\ptext}(\lb,*,i',*)$ is true only if $\sigma[i']$ is matched to the element with $\lb$.
				\item The recursive calls for $\sigma[i+1]$, $\ldots$, $\sigma[i'-1]$ do not change the lower bound. 
				Indeed $\ppattern[i]$ is the rightmost RLMin.
				So $\sigma[i+1]$, $\sigma[i+2]$, $\ldots$, $\sigma[i'-1]$ are RLMax elements. Moreover
				recursive calls for a RLMax do not change the lower bound.
				\item $\PM^{\widetilde{\sigma}}_{\ptext}(\lb,*,i,*)$ sets
				the $\lb$ to $\ptext[j]+1$ and matches $\sigma[i]$ to $\ptext[j]$.
			\end{itemize}
			So $\sigma[i]$ is matched to $\ptext[j]$ and
			$\sigma[i']$ is matched to $\ptext[j]+1$.

@@

				\item  Every recursive call $\PM^{\widetilde{\sigma}}_{\ptext}(\lb,*,i',*)$ is true only if $\sigma[i']$ is matched to the element with value $\lb$.

				\item  The recursive calls for $\sigma[i+1]$, $\ldots$, $\sigma[i'-1]$ do not change the lower bound. Indeed
				from lemma~\ref{lemma:ascentDescentAscent}, $\sigma[i+1]$,  $\ldots$, $\sigma[i'-1]$ are RLMax elements. Finally the recursive calls for RLMax elements do not change the lower bound.

				\item $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i,*)$ sets $\lb$ to $\ptext[j]+1$ and matches $\sigma[i]$ to $\ptext[j]$.

@@

				\item  Every recursive call $\PM^{\widetilde{\sigma}}_{\ptext}(*,\ub,i,*)$ is true only if $\sigma[i]$ is matched to the element with value $\ub$.

				\item  The recursive calls for $\sigma[i+1]$, $\ldots$, $\sigma[i'-1]$ do not change the upper bound. Indeed
				from lemma~\ref{lemma:ascentDescentAscent}, $\sigma[i+1]$,  $\ldots$, $\sigma[i'-1]$ are RLMin elements. Finally the recursive calls for RLMin elements do not change the upper bound.

				\item $\PM^{\widetilde{\sigma}}_{\ptext}(*,*,i',*)$ sets $\ub$ to $\ptext[j]-1$ and matches $\sigma[i']$ to $\ptext[j]$.
